\documentclass[conference]{IEEEtran}
\usepackage{config/ieee-paper}
\input{config/hyphenation}

% Adding references to the document
\addbibresource{IEEEabrv.bib}
\addbibresource{references.bib}

\IEEEoverridecommandlockouts{}
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-taaitles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\input{chapters/authors}

\maketitle

\input{chapters/abstract}

\input{chapters/chapter-1}
\input{chapters/chapter-2}
\input{chapters/chapter-3}


\input{chapters/acknowledgment}

\section*{References}

Please number citations consecutively within brackets\ \cite{b1}. The
sentence punctuation follows the bracket\ \cite{b2}. Refer simply to the reference
number, as in\ \cite{b3}---do not use ``Ref.\ \cite{b3}'' or ``reference\ \cite{b3}'' except at
the beginning of a sentence: ``Reference\ \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at
the bottom of the column in which it was cited. Do not put footnotes in the
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use
``\textnormal{et al.}''. Papers that have not been published, even if they have been
submitted for publication, should be cited as ``unpublished''\ \cite{b4}. Papers
that have been accepted for publication should be cited as ``in press''\ \cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English
citation first, followed by the original foreign-language citation\ \cite{b6}.

\printbibliography{}


\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}
